What is an Ancestral Recombination Graph?

### 2022-01-10 paper.tex
More ancestral graph refs

\section*{Ancestral graphs and stochastic processes}
The coalescent
process~\citep{kingman1982coalescent,kingman1982genealogy,hudson1983testing,
tajima1983evolutionary}

@@

In the theoretical literature, ancestral graphs such as the ARG refer to the
ancestral \emph{process} rather than the outcome of a process.
For example, the Ancestral Selection
Graph~\citep{krone1997ancestral,neuhauser1999ancestral} models selection
as a graph with virtual lineages [etc etc.]. Importantly, the graph structure
of the ASG does \emph{not} correspond to a realised ancestry, but rather
models possible outcomes.

>>>>

\section*{Ancestral graphs and stochastic processes}

% See
The coalescent
process~\citep{kingman1982coalescent,kingman1982genealogy,hudson1983testing,
tajima1983evolutionary}

@@

In the theoretical literature, ancestral graphs such as the ARG refer to the
ancestral \emph{process} rather than the outcome of a process.
\begin{itemize}
\item Ancestral Selection
Graph~\citep{krone1997ancestral,neuhauser1999ancestral} models selection
as a graph with virtual lineages [etc etc.]. Importantly, the graph structure
of the ASG does \emph{not} correspond to a realised ancestry, but rather
models possible outcomes.
Other papers possibly worth citing:\citep{etheridge2009coalescent}
\item Ancestral Gene Transfer Graph~\citep{baumdicker2014infinitely}
\end{itemize}
